%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Acknowledgments Template
%
% The acknowledgments section follows the dedication.  Can be as long or
% short as you wish (``Brevity is the soul of wit''), but generally should
% be a brief, sincere, and professional acknowledgement of everyone who
% played a role in your dissertation (advisor, faculty, fellow students,
% observatory support, etc.).  Funding agencies and fellowships should
% be acknowledged as well.
%
% Updated:
%   2014 May 6 - annual review of grad school formating rules [rwp/osu]
%
%---------------------------------------------------------------------------

\documentclass[main.tex]{subfiles}
\begin{document}

\vspace*{1cm}
\addcontentsline{toc}{chapter}{Acknowledgments}
\begin{center}
{\large Acknowledgments}
\end{center}

\begin{doublespace}

% Where do I even begin?
My gratitude for the support I have received along the journey to this
dissertation is simply too big for words.
I will try nonetheless.
\par
I will start by thanking the Ohio State Department of Astronomy for providing
me with the opportunity of a lifetime.
A number of my colleagues and mentors have described this department as
``greater than the sum of its parts.''
I can think of no better single-phrase explanation, though it takes the
privilege of existing in this environment to understand just how truly special
it is.
I an only assume that there is some kind of magic behind how one group of
people can be so scientifically empowering and so personally welcome at the
same time.
\par
I would especially like to thank my dissertation advisor, David Weinberg, for
being everything I could have hoped for in a mentor and more.
Aside from the unfathomable amount of scientific and professional instruction
you have provided me with, I learned the qualities that make one a fantastic
mentor by experiencing them firsthand.
I would also like to thank Jennifer Johnson and Christopher Kochanek for being
wonderful and brilliant advisors who I am honored to have worked with.
I hope that one day I will provide the same quality of mentorship for my
students as I have received from my committee.
Thank you to many more collaborators, advisors, and co-authors who have taught
me so much, especially Charlie Conroy, Jon Bird, Fiorenzo Vincenzo, Emily
Griffith, Ryan Cooke, Annika Peter, and Kris Stanek.
Thank you to many other members of the deparment who I have been a delight to
work with, especially Wayne Schlingman, Adam Leroy, and Todd Thompson.
\par
I would like to thank my classmates for making my graduate school experience so
personally rewarding.
For pizza on Friday nights, drinks at the barcade, and cherished memories,
thank you Patrick, Tharindu, Emily,
Romy, Rachel, Grace, Dom, Alison, Liam, Jack, Jack, Ari, Josh, Ness, Amanda,
Miqaela, Anusha, Lyra, Kiersten, Sarah, Samson, Caprice, Elvira, Tawny, Deb,
Tyler, Matthias, Becca, Joy, Sebastian, Sinclaire, Michael, Karina, and yet
many more.
I'd like to thank friends from outside of the Astronomy Department for all of
the smiles and laughs over the years, especially Maxim, Trenton, Nick, Kendyll,
Falcon, Andrea, Victor, Cat, Daniel, Elena, Adrian, and Elline.
\par
I'd like to thank my family for their unfailing support.
My parents, for teaching me ambition and disipline and giving me the resources
to succeed.
For your diligence and sacrifices to ensure that I had opportunities to chase
my passions and pursue my dreams.
My sisters, for their guidance, encouragement, advice, and comfort at every
step of the way.
\par
Finally, to Lauren.
I have been chasing the stars my entire adult life, and they led me to you.
You give a man who cannot help but endlessly stargaze a reason to keep an
eye on Earth.
Thank you for your love and support through thick and thin.
I look forward to starting the next chapter of our lives together.








% Where do I even begin? A list of people I'd like to thank for their unfailing
% support:
% \begin{itemize}

% 	\item My committee

% 	\item Other collaborators and advisors

% 	\item My family

% 	\item Lauren

% 	\item Friends and classmates

% \end{itemize}

\end{doublespace}

\end{document}

