%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Vita & Publications Template
%
% The Graduate School requires a Vita in slightly different format than
% the usual Astronomy CV.  The example below is extracted from various
% sources.
%
% The publications list is numbered, and the citation format is DIFFERENT 
% than used in journal articles.  The format lists all authors, the full
% title of the paper, then the journal citation, as follows:
%
%	1. A. Author, B. Author, and C. Author, ``The Full Paper Title'',
%	AJ, 114, 107, (1997)
%	\\
%       \\
%	2. ....
%	\\
%
% Note the double "\\"'s on separate lines used between each entry in the 
% publications list.  This is done to make double-space single-spaced items.  
% Not pretty but it works.
%
% WARNING: NO BLANK LINES ANYWHERE IN THE LIST OF PAPERS!!!
%
%
% Updated:
%   2014 May 6 - annual review of grad school formating rules [rwp/osu]
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[main.tex]{subfiles}
\begin{document}

\vspace*{1cm}
\addcontentsline{toc}{chapter}{Vita}

% Vita - copy lines as required, note how to make blank entries

\begin{center}
{\large Vita}
\end{center}

\begin{singlespace}
\vspace*{0.3cm}
\noindent
\makebox[7cm][l]{May 4, 1995 \dotfill}%
\makebox[5cm][l]{Born -- Iowa City, Iowa}%
\linebreak
\linebreak
\makebox[7cm][l]{2017 \dotfill}%
\makebox[5cm][l]{B.A., Physics \& Astronomy}%
\linebreak
\makebox[7cm][l]{\null}%
\makebox[5cm][l]{Vanderbilt University, Nashville, TN, USA}%
\linebreak
\linebreak
\makebox[7cm][l]{2017 \dotfill}%
\makebox[5cm][l]{Larry Ross Cathey Award}%
\linebreak
\makebox[7cm][l]{\null}%
\makebox[5cm][l]{Vanderbilt Universtiy, Nashville, TN, USA}%
\linebreak
\linebreak
\makebox[7cm][l]{2017 -- 2018 \dotfill}%
\makebox[5cm][l]{University Fellowship}%
\linebreak
\makebox[7cm][l]{\null}%
\makebox[5cm][l]{The Ohio State University, Columbus, OH, USA}%
\linebreak
\linebreak
\makebox[7cm][l]{2018 -- 2022 \dotfill}%
\makebox[5cm][l]{Graduate Research and Teaching Associate}%
\linebreak
\makebox[7cm][l]{\null}%
\makebox[5cm][l]{The Ohio State University, Columbus, OH, USA}
\linebreak
\linebreak
\makebox[7cm][l]{2019 \dotfill}%
\makebox[5cm][l]{M.S., Astronomy}
\linebreak
\makebox[7cm][l]{\null}%
\makebox[5cm][l]{The Ohio State University, Columbus, OH, USA}
\linebreak
\linebreak
\makebox[7cm][l]{2022 \dotfill}%
\makebox[5cm][l]{Ann S. Tuttle Graduate Student Paper Prize}%
\linebreak
\makebox[7cm][l]{\null}%
\makebox[5cm][l]{The Ohio State University, Columbus, OH, USA}%
\linebreak
\linebreak
\makebox[7cm][l]{2022 -- 2023 \dotfill}%
\makebox[5cm][l]{Presidential Fellowship}%
\linebreak
\makebox[7cm][l]{\null}%
\makebox[5cm][l]{The Ohio State University, Columbus, OH, USA}%


%% Publications (see above for format, examples given below).  Note that
%% Grad School standard format for literatur citations differs slightly
%% from our usual journal style, and since the Grad School frankly doesn't 
%% care how we do it in our journals, do it their way or else.

\begin{center}
{\large Publications}
\end{center}

\begin{flushleft}
\textbf{Research Publications}
\end{flushleft}

\begin{enumerate}

	\item J.W. Johnson, D.H. Weinberg, F. Vincenzo, J.C. Bird, E.J. Griffith,
	``Empirical Constraints on the Nucleosynthesis of Nitrogen,'' MNRAS, 520,
	782 (2023).

	\item E.J. Griffith, J.A. Johnson, D.H. Weinberg, J.W. Johnson,
	R. Rodr\'iguez Mart\'inez, K.G. Strassmeier, ``Untangling the Sources of
	Abundance Dispersion in Low-Metallicity Stars,'' ApJ, 944, 47 (2023).

	\item J.W. Johnson, C. Conroy, B.D. Johnson, A.H.G. Peter, P.A. Cargile,
	A. Bonaca, R.P. Naidu, T. Woody, Y.-S. Ting, J.J. Han, J.S. Speagle,
	``Dwarf Galaxy Archaeology from Chemical Abundance and Star Formation
	Histories,'' \textit{under peer review} (2022).

	\item J.W. Johnson, C.S. Kochanek, K.Z. Stanek, ``Binaries Drive High Type
	Ia Supernova Rates in Dwarf Galaxies,'' \textit{under peer review} (2022).

	\item C. Conroy, D.H. Weinberg, R.P. Naidu, T. Buck, J.W. Johnson,
	P.A. Cargile, A. Bonaca, N. Caldwell, V. Chandra, J.J. Han, B.D. Johnson,
	J.S. Speagle, Y.-S. Ting, T. Woody, D. Zaritsky, ``Birth of the Galactic
	Disk Revealed by the H3 Survey,'' \textit{under peer review} (2022).

	\item R.J. Cooke, P. Noterdaeme, J.W. Johnson, M. Pettini, L. Welsh,
	C. Peroux, M.T. Murphy, D.H. Weinberg, ``Primordial Helium-3 Redux: The
	Helium Isotope Ratio of the Orion Nebula,'' ApJ, 932, 60 (2022).

	\item J.W. Johnson, D.H. Weinberg, F. Vincenzo, J.C. Bird, S.R. Loebman,
	A.M. Brooks, T.R. Quinn, C.R. Christensen, E.J. Griffith, ``Stellar
	Migration and Chemical Enrichment in the Milky Way Disc: a Hybrid Model,''
	MNRAS, 508, 4484 (2021).

	\item E.J. Griffith, D.H. Weinberg, S. Buder, J.A. Johnson, J.W. Johnson,
	F. Vincenzo, ``Residual Abundances in GALAH-DR3: Implications for
	Nucleosynthesis and Identification of Unique Stellar Populations,'' ApJ,
	931, 23 (2021).

	\item D.H. Weinberg, et al. (35 co-authors, incl. J.W. Johnson),
	``Chemical Cartography with APOGEE: Mapping Disk Populations with a
	2-process Model and Residual Abundances,'' ApJS, 260, 32 (2021).

	\item F. Vincenzo, D.H. Weinberg, J. Montalb\'an, A. Miglio, S. Khan,
	E.J. Griffith, S. Hasselquist, J.W. Johnson, J.A. Johnson, C. Nitschelm,
	M.H. Pinsonneault, ``CNO Dredge-up in a Sample of APOGEE/Kepler Red Giants:
	Tests of Stellar Models and Galactic Evolutionary Trends of N/O and C/N,''
	\textit{under peer review} (2021).

	\item E.J. Griffith, T. Sukhbold, D.H. Weinberg, J.A. Johnson, J.W. Johnson,
	F. Vincenzo, ``The Impact of Black Hole Formation on Population-Averaged
	Supernova Yields,'' ApJ, 921, 73 (2021).

	\item F. Vincenzo, T.A. Thompson, D.H. Weinberg, E.J. Griffith,
	J.W. Johnson, J.A. Johnson, ``Nucleosynthesis Signatures of Neutrino-Driven
	Winds from Proto-Neutron Stars: A Perspective from Chemical Evolution
	Models,'' MNRAS, 508, 3499 (2021).

	\item E.J. Griffith, D.H. Weinberg, J.A. Johnson, R. Beaton, D.A.
	Garc\'ia-Hern\'andez, S. Hasselquist, J. Holtzman, J.W. Johnson,
	H. J\:onsson, R.R. Lane, D.M. Nataf, A. Roman-Lopes, ``The Similarity of
	Abundance Ratio Trends and Nucleosynthetic Patterns in the Milky Way Disk
	and Bulge,'' ApJ, 909, 77 (2021).

	\item J.W. Johnson, D.H. Weinberg, ``The Impact of Starbursts on Element
	Abundance Ratios,'' MNRAS, 498, 1364 (2020).

	\item J.W. Johnson, A.H. Maller, A.A. Berlind, M. Sinha,
	J.K. Holley-Bockelmann, ``The Secondary Spin Bias of Dark Matter Halos,''
	MNRAS, 486, 1156 (2019).

\end{enumerate}

%% Fields of Study - this is pro forma, leave it alone unless you really
%% did pursue separate fields of study (one of those interdisciplinary
%% things),

\begin{center}
{\large Fields of Study}
\end{center}
Major Field: Astronomy
\end{singlespace}

% \clearpage

\end{document}

